---
title: "index"
author: "Anthony Davidson"
date: "01/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

myPaths <- .libPaths("C:/Program Files/R/R-3.6.2/library")
myPaths <- c(myPaths)
.libPaths(myPaths)  # add new path
.libPaths()

```

# Overview {#over}

The main purpose of this document is to assess the data and combine datasources for `Walker et al. 2019` with a state-space model. To begin with the data needs to be imported as is. The format of this data is in three csv files and a meta=data file??

```{r}
file_location <- system.file(
  "extdata",
  "avian_ecology_bibliography.ris",
  package = "revtools")

library(revtools)
x <- read_bibliography(file_location, return_df = FALSE)
```

Generally, this method leveages the strength of the tidy data approach to combine datasets (Figure 1).

```{r echo=FALSE}
library(DiagrammeR)
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10 layout = circo]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  ScienceResearch; GreyLit; Expert; Knowledge

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  WEbOFScience; Scholar; Scopus
  
  # several 'edge' statements
  Knowledge->Expert->Knowledge
  Knowledge->ScienceResearch
  Knowledge->GreyLit->Knowledge
  ScienceResearch->WEbOFScience
  ScienceResearch->Scholar
  ScienceResearch->Scopus
}
")
```

```{r eval=FALSE, include=FALSE}

# grViz("
# digraph boxes_and_circles {
# 
#   # a 'graph' statement
#   graph [overlap = true, fontsize = 10]
# 
#   # several 'node' statements
#   node [shape = triangle,
#         fontname = Helvetica]
#   Theory
#   
#   # several 'node' statements
#   node [shape = box,
#         fontname = Helvetica]
#   Scale
#   
#   node [shape = box]
#   dateTime; geolocation; counts;
#   Intensity; Intensity;
#   
#   node [shape = circle]
#   Temporal; Spatial; Genetics;
# }")
# #   # several 'edge' statements
# edge []
# Theory->Scale;Scale->Genetics; Scale->Spatial; Spatial->geolocation;
# Scale->Temporal; Temporal->dateTime; Genetics->Intensity;
# dateTime->counts; geolocation->counts; I#IS NOT
# #Scale->Intensity; 

```

## Package uses

Here I explain the use or extention of this work in the future.

### Collect data

```{r}
#small-lit-review..?
```

### Merge and clean orginal data

```{r}
# str(x)
# ??revtools
```

### Restructure to convert to `.bib` file

Using revtools.

```{r}
x2 <- read.csv(("../inst/extdata/joinDavidson2020_walker_manual-mod.csv"))

##function code
file_location1 <- system.file(
  "extdata",
  "joinDavidson2020_walker_manual-mod.csv",
  package = "revtools")

# library(revtools)
# x <- read_bibliography("../inst/extdata/joinDavidson2020_walker_manual-mod.csv", return_df = FALSE)

#this needs to be modified for easy data entry...

```

### Scrap tool to compare additonal information.

```{r}
#small-lit-review..?
```

###

