---
title: "index"
author: "Anthony Davidson"
date: "01/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

myPaths <- .libPaths("C:/Program Files/R/R-3.6.2/library")
myPaths <- c(myPaths)
.libPaths(myPaths)  # add new path
.libPaths()

```

# Overview {#over}

The main purpose of this document is to assess the data and combine datasources for `Walker et al. 2019` with a state-space model. To begin with the data needs to be imported as is. The format of this data is in three csv files and a meta=data file??

```{r}
file_location <- system.file(
  "extdata",
  "avian_ecology_bibliography.ris",
  package = "revtools")

library(revtools)
x <- read_bibliography(file_location, return_df = FALSE)
```

## 1. Merge and clean orginal data

```{r}
str(x)
??revtools
```

## 2. Restructure to convert to bib file

Using revtools.

```{r}
x2 <- read.csv(("../inst/extdata/joinDavidson2020_walker_manual-mod.csv"))

##function code
file_location1 <- system.file(
  "extdata",
  "joinDavidson2020_walker_manual-mod.csv",
  package = "revtools")

# library(revtools)
# x <- read_bibliography("../inst/extdata/joinDavidson2020_walker_manual-mod.csv", return_df = FALSE)

#this needs to be modified for easy data entry...

```


## 3. Scrap tool to compare additonal information.



